---
format:
  dashboard:
    orientation: columns
aliases: 
  - home.html
project:
  output-dir: docs/
---

```{r}
library(htmltools)
```

## {.sidebar}
Dashboard contains the materials for the **Baltimore Introductory Spectral Cytometry Course 2025**.

**Navigation:**

From the Home page, click on your instrument and the corresponding day to navigate to the corresponding interactive materials. 

**About**

This course is run by the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/), an ISAC recognized Shared Resource Laboratory. 

For additional flow cytometry resources, please visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)


## First Row {height="50%"}

### Cytek Aurora 3L {width="50%"}

::: {.card title="" width="33%"}

:::

```{r}
#| content: valuebox
#| title: "Cytek Aurora 3L"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Day1_3L.html'>Day 1</a></li>
  <li><a href='Day2_3L.html'>Day 2</a></li>
  <li><a href='Day3_3L.html'>Day 3</a></li>
  <li><a href='Day4_3L.html'>Day 4</a></li>
  <li><a href='Day5_3L.html'>Day 5</a></li>
</ul>
")
```

### Cytek Aurora 5L {width="50%"}

::: {.card title="" width="33%"}

:::

```{r}
#| content: valuebox
#| title: "Cytek Aurora 5L"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Day1_5L.html'>Day 1</a></li>
  <li><a href='Day2_5L.html'>Day 2</a></li>
  <li><a href='Day3_5L.html'>Day 3</a></li>
  <li><a href='Day4_5L.html'>Day 4</a></li>
  <li><a href='Day5_5L.html'>Day 5</a></li>
</ul>
")
```

## Second Row {height="50%"}

### Cytek Aurora 4L {width="50%"}

```{r}
#| content: valuebox
#| title: "Cytek Aurora 4L"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Day1_4L.html'>Day 1</a></li>
  <li><a href='Day2_4L.html'>Day 2</a></li>
  <li><a href='Day3_4L.html'>Day 3</a></li>
  <li><a href='Day4_4L.html'>Day 4</a></li>
  <li><a href='Day5_4L.html'>Day 5</a></li>
</ul>
")
```

::: {.card title="" width="33%"}

:::

### Cytek Aurora CS {width="50%"}

```{r}
#| content: valuebox
#| title: "Cytek Aurora CS"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Day1_CS.html'>Day 1</a></li>
  <li><a href='Day2_CS.html'>Day 2</a></li>
  <li><a href='Day3_CS.html'>Day 3</a></li>
  <li><a href='Day4_CS.html'>Day 4</a></li>
  <li><a href='Day5_CS.html'>Day 5</a></li>
</ul>
")
```

::: {.card title="" width="33%"}

:::
